Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-29 paper/high-assurance-contracts.tex
Add guard on pre in contract

    eq preIsPending : bool = pre(isPending);*\label{line:mon-pre-pending}*
    eq isPending : bool = Since(not rsp, req and not rsp);*\label{line:mon-pending}*
    eq latency : int = 0 -> (if req then 0 else pre(latency) + 1);*\label{line:mon-latency}*

>>>>

    eq preIsPending : bool = false -> pre(isPending);*\label{line:mon-pre-pending}*
    eq isPending : bool = Since(not rsp, req and not rsp);*\label{line:mon-pending}*
    eq latency : int = 0 -> (if req then 0 else pre(latency) + 1);*\label{line:mon-latency}*
